#Objective :Building Models(SVM and LDA) to predict the customers who will cancel their service


#Reading the Data
```{r}
setwd("D:/Assignments PGBABi/Projects/SVM and LDA Project")

library(readxl)
data<-read_excel("GA_Dataset.xlsx",sheet=2)
```

#Understand Data
```{r}
str(data)
```
#Churn,ContractRenewal,DataPlan has to be converted into :factor

```{r}
data$Churn<-as.factor(data$Churn)
data$ContractRenewal<-as.factor(data$ContractRenewal)
data$DataPlan<-as.factor(data$DataPlan)

summary(data)
```

#checking for missing data/duplicate data
```{r}
anyDuplicated(data) #no duplicate data
colSums(is.na(data)) #no missing Data in any column
```
#check for clASS Imbalance
```{r}
prop.table(table(data$Churn))
```


#Quick Visual EDA
```{r}

library(DataExplorer)
plot_intro(data)
plot_missing(data)
plot_histogram(data)
plot_boxplot(data,by="Churn")
plot_bar(data)
install.packages("corrgram")
library(corrgram)
corrplot(corrgram(data))

```
#Bivariate/Multivariate Analysis
```{r}
library(ggplot2)
ggplot(data)+
  geom_bar(aes(x=DataPlan,fill=Churn,stat="identity"))
colnames(data)
```


```{r}
#Anova
attach(data)
#correlation between categorical and continuous variable
basic_model=aov(DataUsage~Churn)
summary(basic_model)

#correlation between two categorical variables
chisq.test(table(Churn,ContractRenewal))
chisq.test(table(Churn,DataPlan))

```







#Data Split into test and train
```{r}
library(caTools)
set.seed(127)
split=sample.split(data$Churn,SplitRatio =0.7)
trainData<-subset(data,split==TRUE)
testData<-subset(data,split==FALSE)
```

#Checking Split
```{r}
prop.table(table(trainData$Churn))
prop.table(table(testData$Churn))
```

#Build Model:SVM.
```{r}
library(e1071)


obj <- tune(svm, Churn~., data = trainData, 
              ranges = list(gamma = 2^(-1:1), cost = (1:10)),
              tunecontrol = tune.control(sampling = "fix")
             )
summary(obj)

SVMModel1<-svm(Churn~.,data=trainData,kernel="radial",scale=TRUE, cost = 2, gamma = 0.5) 
summary(SVMModel1)
Prediction1<-predict(SVMModel1)
cm1<-table(Actual=trainData$Churn,Predicted=Prediction1)
Accuracy_train1<-(cm1[1,1]+cm1[2,2])/(cm1[1,1]+cm1[1,2]+cm1[2,1]+cm1[2,2]) 
Accuracy_train1
cm1


SVMModel2<-svm(Churn~.,data=trainData,kernel="linear",scale=FALSE, cost = 2, gamma = 0.5)   
summary(SVMModel2)
Prediction<-predict(SVMModel2)
table(Actual=trainData$Churn,Predicted=Prediction)

SVMModel3<-svm(Churn~.,data=trainData,kernel="radial",scale=FALSE, cost = 2, gamma = 0.5)   
summary(SVMModel3)
Prediction<-predict(SVMModel3)
table(Actual=trainData$Churn,Predicted=Prediction)

SVMModel4<-svm(Churn~.,data=trainData,kernel="polynomial",scale=FALSE, cost = 2, gamma = 0.5)  
summary(SVMModel4)
Prediction<-predict(SVMModel4)
cm4 = table(Actual=trainData$Churn,Predicted=Prediction)
Accuracy_train1<-(cm4[1,1]+cm4[2,2])/(cm4[1,1]+cm4[1,2]+cm4[2,1]+cm4[2,2]) 
Accuracy_train1

#test Data(Model 3 is complete overfit model therefore using model1)
Prediction_testData<-predict(SVMModel1,newdata=testData)
cm_test<-table(Actual=testData$Churn,Predicted=Prediction_testData)
Accuracy_test<-(cm_test[1,1]+cm_test[2,2])/(cm_test[1,1]+cm_test[1,2]+cm_test[2,1]+cm_test[2,2]) 
Accuracy_test

```
#Build Model : LDA
```{r}
library(DiscriMiner)
names(trainData)
X<-trainData[,-c(1,4,3)]
#LDA on train Data
Mahalanabois=linDA(X,trainData$Churn) #error rate14%
Mahalanabois


Mahalanabois2=linDA(X,trainData$Churn,validation = "crossval") #error rate14%
Mahalanabois2


learning=c(which(trainData$Churn==0),which(trainData$Churn==1))
testing=c(which(testData$Churn==0),which(testData$Churn==1))
length(testing)
#on Test Data
linDA(X,trainData$Churn,validation = "learntest",learn = learning,test=testing)          #errorrate:13%

```

